<!--
Chapter 1. The {#rmd-basics} text after the chapter declaration will allow us to link throughout the document back to the beginning of Chapter 1.  These labels will Chapter 1. automatically be generated (if not specified) by changing the spaces to hyphens and capital letters to lowercase.  Look for the reference to this label at the beginning of Chapter 2.
-->

# Chapter 1: Marine Ecology in a Changing World: Physiological Responses to Enivronmental and Global Change {-}

 Organisms and ecosystem processes alike are governed by the ability to perform and function under a mosaic of complex interactions, as each acts to influence one another noncontemporaneously and contemporaneously through direct and indirect feedback loops (Levin \& Paine, 1974; Paine, 1980). The relationship between organisms and environments varies temporally and spatially, influenced by a myriad of dynamic biotic and abiotic drivers (Connell, 1961; Connell \& Slatyer, 1977; Helmuth et al., 2006; Kroeker et al., 2017; Menge \& Sutherland, 1987; Stenseth et al., 2002). Environmental drivers are abiotic parameters that influence organisms and environments across a spectrum ranging from enhancing and optimal to stressful conditions (Boyd \& Hutchins, 2012; Côté et al., 2016). For example, within marine ecosystems, the combination of oceanographic processes and local coastal geography creates patterns and variability in temperature, flow, pH, dissolved oxygen, etc., that impact the structure and processes of communities on scales from microscale to macroscale (Deser et al., 2010; Hofmann \& Todgham, 2010). Such heterogeneous patterns, attributed to natural variation, create complex and stochastic gradients that shape ecological communities and influence physiological processes within and between organisms, mediated through physiological mechanisms, such as phenotypic plasticity and acclimatization (Helmuth et al., 2006; Hofmann \& Todgham, 2010; Tomanek \& Helmuth, 2002). Environmental changes across gradients and variability within abiotic factors result in physiological trade-offs due to alterations within the energetic allocation and the partitioning of metabolic activity (Brown et al., 2004; Pörtner \& Farrell, 2008). 

 Organisms and environments actively codetermine one another (Levins \& Lewontin, 1985; Corris, 2020). Organisms are the subjects and objects of ecological change, shaping their milieu through activities (e.g., respiration, calcification, photosynthesis, herbivory, and predator-prey interactions) that transform and reconfigure the biological, physical, and chemical properties of the environment (Hegel, 1830; Levins \& Lewontin, 1985; Lewontin, 1983; Silbiger \& Sorte, 2018). Extensive research has demonstrated that organisms undergo processes that alter the statistical variability of the environments they occupy (Allemand et al., 2011; Estes \& Palmisano, 1974; Lewontin, 1983; Silbiger \& Sorte, 2018), such as influencing atmospheric oxygen levels (Berkner et al., 1965), constructing biogenic structures (Silbiger \& Sorte, 2018), and altering seawater biogeochemistry through physiological processes (Silbiger \& Sorte, 2018; Ricart et al., 2021). Simultaneously, as organisms undergo these processes, they must physiologically adapt to the natural variability (e.g., diurnal, daily, and seasonal) of the stochastic environments they inhabit whilst withstanding the energetic demands imposed by these fluctuations. In a geological epoch of rapid environmental change, it is increasingly imperative to understand the extent to which organisms can respond to environmental variability across multiple drivers of spatiotemporal change (Connell, 1961; Helmuth et al., 2006; Kroeker et al., 2017; Stenseth et al., 2002). Understanding the energetic constraints of physiological responses to multiple drivers of change is perhaps the \textit{sine qua non} for inferring how changes in organismal-level processes may scale to alter energetic flow within ecological communities and, consequently, ecological processes (Odum, 1968; Pörtner \& Farrell, 2008).

 Metabolism comprises the total sum of biological and chemical processes in converting energetic resources and materials into biomass and activity (Brown et al., 2004; Von Bertalanffy, 1957). Metabolism is primarily governed by an organism’s body size, temperature and the labor an organism undergoes, with body size dictating energetic demands and temperature directly affecting the kinetic energy of biological processes (Brown et al., 2004; Gillooly et al., 2002; O’Connor et al., 2007). Furthermore, metabolic rates—the rate at which organisms transform energy and materials—are equivalent to the rate at which they respire, as cellular processes of respiration scale up to the organismal level to mediate the conversion of nutrients into energy in the form of adenosine triphosphate (ATP). The process of cellular respiration, which involves the consumption of oxygen (O$_2$) to produce energy in the form of adenosine triphosphate (ATP) through mitochondrial activity, can be described as follows (Babcock \& Wikström, 1992; Hochachka \& Somero, 2002):

\begin{equation}
\label{eq:respiration}
\mathrm{C_6H_{12}O_6 + 6O_2 \leftrightarrow 6CO_2 + 6H_2O + ATP}
\end{equation}

Thus whole-organism measurements of respiratory rates (O$_2$ consumption) act as a proxy for an organism's overall rate of cellular respiration and energetic demand.

## Physiological Energetics in Response to Multiple Drivers of Change {-}

 Temperature controls the tempo and rhythm of ecological processes, serving as the fundamental driver in determining the rate of biological processes (Angilletta, 2009). An increase in temperature exponentially accelerates biochemical reaction rates, metabolic rates, and nearly all other rates of biological activity (Brown et al., 2004; Dell et al., 2011; Hochachka, 1967; Hochachka \& Somero, 2002; Huey \& Stevenson, 1979; Levins, 1969; Somero, 1995). At the cellular level, temperature exerts its force by modulating the kinetic energy of molecules, altering the enzymatic activity essential for catalyzing reactions, and directly impacting the rates of biochemical reactions critical for metabolic processes (Angilletta, 2009; Angilletta et al., 2010; Brown et al., 2004; Somero, 2020). These temperature-dependent kinetic dynamics are encapsulated by the Boltzmann–Arrhenius relationship (2), which quantitatively describes the temperature dependence of reaction rates governing chemical and biological processes through activation energy and temperature (Arrhenius, 1915; Boltzmann, 1872). 

\begin{equation}
\label{eq:boltzmann}
k = A \cdot e^{-\frac{E_a}{k_B \cdot T}}
\end{equation}

 where $k$ represents the rate constant, $A$ represents the pre-exponential factor, $E_a$ represents the activation energy in electron volts (eV), $k_B$ is the Boltzmann constant in eV K$^{-1}$ (approximately $8.62 \times 10^{-5}$ eV$\cdot$K$^{-1}$), and $T$ is the absolute temperature in Kelvin.

The Arrhenius relationship is often reformulated to model biological rate processes as a function of temperature relative to a reference temperature:

\begin{equation}
\label{eq:arrhenius}
R(T) = R_{T_{\text{ref}}} \cdot e^{-\frac{E_a}{k_B} \left( \frac{1}{T} - \frac{1}{T_{\text{ref}}} \right)}
\end{equation}

 Wherein $R(T)$ is the metabolic rate of a biological process as a function of temperature, $R_{T_{\text{ref}}}$ represents the baseline metabolic rate at the reference temperature $T_{\text{ref}}$, $E_a$ represents the activation energy in electron volts (eV), $k_B$ is the Boltzmann constant in eV K$^{-1}$ (approximately $8.62 \times 10^{-5}$ eV$\cdot$K$^{-1}$), $T$ is the absolute temperature in Kelvin, $T_{\text{ref}}$ is the standardization temperature at which rates are not inactivated by either high or low temperatures, $k$ is the rate constant, $A$ represents the pre-exponential factor, and $R$ represents the universal gas constant ($8.314$ J mol$^{-1}$ K$^{-1}$).

 The regulatory influence of temperature on metabolic processes within cells extends beyond the cellular level, influencing higher levels of biological organization and scaling up to impact individuals, populations, and species interactions (Brown et al., 2004; Hochachka \& Somero, 2002). The Metabolic Theory of Ecology (MTE) provides a mechanistic framework for understanding changes in energetic expenditure, interlinking ecological processes and organismal metabolism (Brown et al., 2004). The MTE posits that metabolic rates follow predictable patterns with body mass and temperature, which are governed by enzyme reaction rates (Brown et al., 2004; Gillooly et al., 2001) and can be mathematically expressed as: 

\begin{equation}
\label{eq:MTE}
R(T) = b_0 M^{3/4} e^{-\frac{E_a}{k_B T}}
\end{equation}

 Here, $b_0$ is a normalization constant—including the effect of body size $M^{3/4}$ scaling—$T$ is absolute temperature (in K), $k_B$ is the Boltzmann constant ($8.62 \times 10^{-5}$ eV$\cdot$K$^{-1}$), and activation energy $E_a$ (eV) which results in the mass-corrected metabolic rate $R(T)$. 

 Particularly impacted by temperature constraints are ectothermic species, which comprise the vast majority of species, including fish, reptiles, and invertebrates. These species typically rely on external environmental temperatures and physiological plasticity (i.e., poikilothermy) to regulate internal body temperature and metabolic processes (Angilletta et al., 2002, 2010; Clarke \& Pörtner, 2010; Huey \& Kingsolver, 1989; Seebacher et al., 2015). For example, consider the impact of temperature on the size of ectothermic organisms, a relationship that results in faster developmental rates as temperatures increase, yet maturity at smaller sizes, demonstrating a phenomenon known as the temperature-size rule (Atkinson, 1994; Kingsolver \& Huey, 2008). Or more species-specific constraints, such as sea turtles whose reproductive biology is governed by temperature-dependent sex determination (TSD), where a 1$^\circ$C increase above the pivotal temperature can skew the population's birth rates entirely to one sex (Bull, 1985; Gammon et al., 2020).

 Research demonstrating the governing force of temperature on biological processes and metabolic activity is well documented, spanning from organismal-level implications that result in alterations in growth, consumption, and reproductive rates (Gillooly et al., 2001; Kordas et al., 2011; Kroeker \& Sanford, 2022) to species-level consequences such as changes in species interactions and distribution ranges (Pinsky et al., 2013; Sanford, 1999). Across species and ecosystems, there is clear evidence that increases in environmental temperature speed up the rate of metabolic activity, with warmer internal body temperatures necessitating disproportionately more energy per unit of time to maintain homeostasis (Gillooly et al., 2001; Huey \& Kingsolver, 1989; Poloczanska et al., 2016; Pörtner \& Knust, 2007). Furthermore, species evolve to endure a spectrum of thermal conditions for physiological processes, with local populations adapting and acclimatizing to a range within localized conditions (Huey \& Kingsolver, 1989; Sinclair et al., 2016). However, survival, fitness, and population densities are significantly affected when temperatures exceed a species’ acclimatization limits and optimal temperature ranges (Hochachka \& Somero, 2002). Additionally, it is important to recognize that, while temperature plays a critical role in influencing physiological processes and rates, other environmental drivers concurrently catalyze a myriad of interactive effects (Côté et al., 2016).

 Variability in the oceanic carbonate system is another integral determinant of marine organismal and ecosystem processes, as pH plays a vital role in regulating biochemical pathways and maintaining the internal acid-base balance of marine organisms (Gaylord et al., 2015; Kroeker, Gambi, et al., 2013; Kroeker, Kordas, et al., 2013). Variations in the oceanic carbonate system are often influenced by a series of physical and biological processes occurring near coastlines such as upwelling, biological activity, and freshwater input (Garcıa-Reyes \& Largier, 2012; Silbiger et al., 2020; Silbiger \& Sorte, 2018; Sydeman et al., 2014). Biophysical feedback loops also modulate oceanic carbonate chemistry, particularly in shallow systems when community-level respiration rates surpass photosynthetic activity at night, leading to nighttime dissolution lows and further reducing seawater pH (Gaylord et al., 2019; Kwiatkowski et al., 2016; Silbiger \& Sorte, 2018).

 At the cellular level of organismal physiology, shifts in seawater pH can rapidly translate into changes in gene expression, modulation of metabolic and cellular pathways, and alterations in the structure and function of proteins (Hochachka \& Somero, 2002); if drastic enough, these changes can incur substantial energetic costs and necessitate shifts in energetic allocation (Luan et al., 2023; Michaelidis et al., 2005). Shifts in the physiochemistry of seawater that alter the ionic concentration gradient, such that extracellular pH is lower than intracellular pH, result in a higher concentration of hydrogen ions (H+) inside the cell than outside and incur costs for ionic transport mechanisms (Pörtner \& Farrell, 2008). Consequently, these shifts necessitate an increase in the energy expended to drive the proton efflux of hydrogen ions (H+) from the cell to maintain homeostasis (Taylor et al., 2012). These cellular-level impacts extend to the organism level, where reductions in pH can impair olfactory sensing, modify behavioral interactions, affect neuromodulation, and alter oxygen diffusion through hypercapnia (Jellison et al., 2016; Lefevre, 2016; Munday et al., 2009).

 Changes in seawater physicochemical parameters that lead to declines in carbonate saturation and pH are associated with detrimental effects on physiological processes, which include reductions in growth rates, decreases in calcification rates, and diminished structural integrity of calcified structures (Hofmann \& Todgham, 2010; Kroeker et al., 2013). Declines in seawater calcium carbonate ion concentrations significantly increase the costs associated with transforming seawater's chemical properties into calcified structures (Spalding et al., 2017), impacting the formation of calcium carbonate-based skeletal structures in echinoderms, exoskeletons in crustaceans, and shells in gastropods (Barclay et al., 2019; Doney et al., 2009; Gazeau et al., 2007; Hoegh-Guldberg et al., 2007; Orr et al., 2005; Whiteley, 2011). Yet speciesspecific differences exist in the energetic costs associated with calcification (Barclay et al., 2019; Gaylord et al., 2019), the chemical properties involved in creating structures (e.g., calcite versus aragonite, see (Barclay et al., 2019), and the ability to control acid-base regulation (Doney et al., 2009; Kroeker, Kordas, et al., 2013). For instance, variations in calcification strategies across taxa, such as precipitating shells, spines, and skeletons utilizing calcite versus aragonite, can significantly influence the energetic costs associated with calcification (Barclay et al., 2019). This species-specific variation derives from the structural integrity of the precipitates used to build calcified structures as well as differences in solubility, with the former impacting predation susceptibility and the latter affecting susceptibility to dissolution (Barclay et al., 2019; Ries et al., 2009). Consequently, changes in the seawater carbonate chemistry attributed to pH affect species differently, impact interactions between species, and, and ultimately community structure and ecosystem processes (Gaylord et al., 2015; Kroeker et al., 2013; Kroeker et al., 2013). Therefore, studying how different combinations of environmental drivers affect organismal physiology has ecosystem-level implications (Kroeker, Sanford, et al., 2014; Tomanek \& Helmuth, 2002).

 Multiple environmental drivers—variation in temperature, changes in oxygen saturation, desiccation stress, and seawater carbonate dynamics—directly impact the physiological processes of marine organisms (Todgham et al., 2005) and interact to shape the functioning of ecosystems (Harborne, et al., 2017), underscoring the need for a paradigm shift in our approach to understanding the complexities of future scenarios (Kroeker et al., 2017; Woodwell, 1970). Environmental drivers interact in complex ways, potentially amplifying or mitigating impacts on organismal energetic requirements and leading to unexpected outcomes known as "ecological surprises" (Kroeker et al., 2017; Paine et al., 1998). For instance, the cumulative impact of two drivers acting together may result in outcomes that are equivalent to their sum (additive effect), less than their additive effect (antagonistic interaction), or greater than their additive effect (synergistic interaction) (Côté et al., 2016). Given that metabolic responses and physiological systems vary within and between species, and environmental drivers interact in complex ways, it is important to identify the mechanisms that underpin organism-level physiological capacities. Moreover, alterations within an individual organisms’ physiological performance are ecologically significant because alterations can scale up to affect ecosystem function (Kroeker, Gambi, et al., 2013; Kroeker \& Sanford, 2022). Investigating how multiple abiotic factors influence organismal physiology holds implications for ecosystem-level processes (Tomanek \& Helmuth, 2002). Therefore, building a mechanistic understanding regarding the combined impacts of ocean warming and acidification on marine organisms is integral for reliable projections of how climate change may continue to affect marine organisms (Carey et al., 2016).
 
## Intertidal Ecosystems as Model Systems of Change {-}

 Carved out over centuries at the interface between land and sea, intertidal rock pools reveal the biophysical phenomena governing the underlying logic of the universe. For millennia, communities, philosophers, scientists, thinkers, and artists have been captivated by tide pools and driven to uncover the underlying principles and logic that allow the lifeforms in these highly variable environments to persist, as well as the abundance of wealth and knowledge these ecosystems offer humanity (Erlandson et al., 2007, 2015; Paine \& Gould, 1977; Raffaelli \& Hawkins, 1996; Ricketts et al., 1985; Sharpley \& Koehn, 2022; Toniello et al., 2019). The steep gradients of the rocky intertidal zone, both abiotic (e.g., temperature) and biotic (e.g., ecological linkages), serve as a microcosmic example of the environmental gradients that structure ecosystems; the changes over just a few meters in the intertidal zone are analogous to the physical and biological forces that organize entire mountain ranges.(Dayton, 1971; Paine, 1969; Somero, 2002; Stenseng et al., 2005). Intertidal ecosystems cycle from terrestrial to marine states, undergoing drastic physical changes between tides on both temporal and spatial scales; this variability makes them ideal models for understanding how organisms withstand and adapt to change. (Connell, 1961; Jellison et al., 2022; Kwiatkowski et al., 2016; Paine, 1969; Tomanek \& Helmuth, 2002). Additionally, intertidal ecosystems have been a prime location to test ecological theories, resulting in an extensive record of experimental manipulations and seminal work on ecological principles (Connell, 1972; Connolly \& Roughgarden, 1998; Lubchenco, 1978; Menge \& Sutherland, 1987; Paine, 1966; Paine \& Gould, 1977). Some of these theories include the keystone species concept, foundation species concept, intermediate disturbance hypothesis, intertidal zonation patterns, and the role of competition and cooperation in community structure (see studies above).

 Rocky intertidal ecosystems are among Earth's most stochastically variable and physically harsh environments, wherein organisms endure transformations in the physical and chemical properties of rock pools due to tidal, diurnal, and seasonal changes (Denny \& Wethey, 2001; Helmuth et al., 2006; Tomanek \& Helmuth, 2002; Wolfe et al., 2020). Throughout tidal cycles, organisms contend with fluctuations in temperature, oxygen availability, salinity, pH, and moisture during transitions between aerial and aquatic phases (Denny \& Wethey, 2001; Kunze et al., 2021; Somero, 2002; Tomanek \& Helmuth, 2002). Intertidal ecological research has demonstrated that temperature is the primary driver of vertical zonation and latitudinal distribution patterns, with thermal stress limiting the upper zonation of species and biotic interactions determining lower zonation limits (Connell, 1961; Helmuth et al., 2006; Somero, 2002; Sorte et al., 2019; Stenseng et al., 2005). Intertidal organisms must withstand thermal variability, resulting in environmental temperature fluctuations of up to $10^{\circ}$--$20^{\circ}$C within a 24-hour span (Helmuth, 1999; Helmuth et al., 2006, 2016; Kunze et al., 2021). Additionally, pH swings in tide pools can exceed 0.75 units during periods when community-level respiration rates surpass photosynthetic rates, leading to daily variability that exceeds pH conditions anticipated in the future (Jellison et al., 2016; Kunze et al., 2021; Kwiatkowski et al., 2016; Silbiger \& Sorte, 2018). These dynamic environments have shaped the eco-evolutionary trajectories of species (Katz et al., 2004), leading to complex physiological adaptations such as anaerobic metabolism and metabolic depression, which makes these organisms ideal models for studying the impacts of environmental change on physiology (Michaelidis et al., 2005b; Pörtner, 2010). Thus, studying rocky intertidal ecosystems can provide a glimpse towards the future. 

\newpage

## Ocean Acidification \& Warming, Dual Consequences of Anthropogenic Induced CO\texorpdfstring{$_2$}{2} {-}

```{r fig_1_1_atmospheric_co2, results='asis', echo=FALSE}
cat("
\\begin{figure}[ht]
  \\centering
  \\includegraphics[width=1\\textwidth]{", here::here("figures", "chapter1", "Fig_1_1_Atmospheric_CO2.png"), "}
  \\caption[Monthly atmospheric CO\\textsubscript{2} concentration (ppm), Mauna Loa Observatory, Hawaii (1958--2024).]{Keeling curve with annual variation inset (differences from annual average) illustrating planetary-level photosynthesis and respiration exerting an influence on atmospheric CO\\textsubscript{2}. Data from NOAA Global Monitoring Laboratory.}
  \\label{fig:atmospheric_co2}
\\end{figure}
")
```


 As the atmospheric carbon dioxide (CO$_2$) concentration continues to surpass the limits of the earth system, marine organisms will be forced to endure profound transformations of the environment, from shifts in temperature to altered seawater biogeochemistry that will layer on top of natural variability within ecosystems (Figure~\ref{fig:atmospheric_co2}) (Pörtner \& Farrell, 2008; Richardson et al., 2023). Since the beginning of the 20th century, the global mean sea surface temperature (SST) has increased by 0.88 [0.68--1.01]$^\circ$C, and is further projected to warm by 2.89$^\circ$C [2.01--4.07$^\circ$C] at the end of the century, which surpasses the thermal tolerance limits of many marine species (Bay, Rose, Logan, \& Palumbi, 2017; Fox-Kemper et al., 2021; Kikstra et al., 2022). Concurrently, the ocean has absorbed approximately $30\%$ of all anthropogenic CO$_2$ emissions (Feely et al., 2004), resulting in significant alterations in seawater pH (Equations:~\ref{eq:co2_dissolution}, \ref{eq:bicarbonate_equilibrium}, and \ref{eq:carbonate_equilibrium}).

\begin{equation}
\begin{aligned}
\ce{CO2(g)} \\[-0.8em]
\ce{\downarrow} \ \ \ \ \ \\[-0.8em]
\ce{CO2(aq)}
\end{aligned}
\label{eq:co2_dissolution}
\end{equation}

\begin{equation}
\ce{CO2(aq) + H2O(l) <=> H+ (aq) + HCO3^- (aq)}
\label{eq:bicarbonate_equilibrium}
\end{equation}
\vspace{-\baselineskip}
\begin{equation}
\ce{HCO3^- (aq) <=> H+ (aq) + CO3^{2-} (aq)}
\label{eq:carbonate_equilibrium}
\end{equation}

 The equation above illustrates the reaction that unfolds as CO$_2$ diffuses into seawater to produce carbonic acid (H$_2$CO$_3$) and subsequently dissociates into bicarbonate ions (HCO$_3^-$) and hydrogen ions (H$^+$) (Feely et al., 2004)(Equations:~\ref{eq:co2_dissolution}, \ref{eq:bicarbonate_equilibrium}, and \ref{eq:carbonate_equilibrium}). Further dissociation of bicarbonate ions engenders additional hydrogen ions (H$^+$) alongside carbonate ions, effectively increasing the acidity of seawater.

 Ocean warming (OW) and ocean acidification (OA) are not isolated phenomena; they share a common origin and are byproducts of an extract economy built on fossil fuel (Wolff et al., 2015; Licker et al., 2019; Healy et al., 2019). In a rapidly changing world, their combined impacts on organismal physiology necessitate a more nuanced understanding as multiple drivers of change will act interactively (Côté et al., 2016; Darling \& Côté, 2008). Moreover, the impacts of OW and OA will not be consistent across geographic regions, leading to differential effects that will modify already variable spatial and temporal environments (Gruber, 2011; Kroeker et al., 2016). Organisms undergoing physiologically stressful conditions that result in elevated metabolic costs and restricted aerobic capacity (limited aerobic scope) could be further limited by the inability to counteract additional stressors, yet these instances are dependent upon magnitude and context (Sokolova, 2013; Todgham \& Stillman, 2013). For example, a +12°C thermal shock improved the hypoxia tolerance of tidepool sculpins (Oligocottus maculosus), while a +15°C shock significantly reduced the resilience of the fish to additional stressors (Todgham et al., 2005; Todgham \& Stillman, 2013). Thus building a mechanistic understanding of how the combined impacts of OW and OA affect marine organisms across an environmental gradient is integral for reliable projections of how climate change may impact marine species (Kroeker et al., 2017; Pörtner, 2012a). Despite the increasing emphasis on multi-driver and multi-species studies, a mechanistic understanding of the nonlinear responses regarding the interactive effects of OA and OW remains a critical knowledge gap (Kroeker et al., 2017). 

 The coastal and adjacent waters of the northeastern Pacific Ocean, known as the California Current System (CCS), present a particularly advantageous living laboratory for enhancing our capacity to comprehend the impacts of multiple drivers of global change on organismal physiology and energetics (Hofmann, Evans, Kelly, Padilla-Gamiño, Blanchette, Washburn, Chan, McManus, Menge, \& Gaylord, 2014; Somero et al., 2016). The CCS is an extensively-studied marine ecosystem where long-term data and research illustrate the impacts of climatic variability (e.g. Pacific Decadal Oscillation and El Niño Southern Oscillation (García‐Reyes \& Largier, 2012)) on abiotic factors, such as temperature and carbonate chemistry, with associated changes already impacting organismal performance (Chavez et al., 2003; Connolly \& Roughgarden, 1998; Feely et al., 2008, 2012; Kroeker, Gambi, et al., 2013; Mekkes et al., 2021; Somero et al., 2016). Temperature logger (Onset Tidbit V2 Temp Data Logger; Onset Computer Corp. UTBI-001) data from Multi-Agency Rocky Intertidal Network (MARINe) and Partnership for Interdisciplinary Studies of Coastal Oceans (PISCO) bolted to the substrate within a long-term intertidal monitoring site at Port Fermin, Los Angeles, CA from August–September 2022, reveal an average ocean water temperature of 17.31°C and a maximum ocean water temperature of 23.79°C during high tide, contrasting with a slightly higher mean aerial temperature of 17.41°C, which can soar to a maximum of 33.73°C during low tide (Multi-Agency Rocky Intertidal Network (MARINe) et al., 2023). These findings highlight the natural variability and acute thermal stress that intertidal organisms are subjected to within the southern California Bight region of the CCS, particularly during aerial exposure. Furthermore, despite the inherent natural variability present within California coastal ecosystems, a comprehensive analysis of the measurements of coastal ocean temperatures in the Southern California Bight over the past century (1917-2017) reveals significant increases in nearshore temperatures, delineating a warming trend of 1.24 ° C per century at the surface and 1.67 ° C per century in bottom waters (Rasmussen et al., 2020). Moreover, the longest running record of carbonate system dynamics in the CCS reveals a 37-year record of ocean acidification in the Southern California region with an expected decrease in pH of -0.15 ± 0.01 units per century (Wolfe et al., 2023). These concurrent changes and inherent variability make the CCS a particularly important location for studying the impacts of multiple global changes. 

## Comparative Physiology as a Means to Delineate Responses to Multiple Drivers of Change {-} 

 The integration of thermal performance curves (TPC) with the metabolic theory of ecology, which posits that the energetic expenditure of organisms is fundamentally linked to environmental temperatures, enables ecologists to forecast changes in species distributions and community structures as global temperatures continue to rise against a backdrop of acidification (Brown et al., 2004; Kroeker et al., 2017; Kroeker, Gaylord et al., 2014). The use of performance curves can help to quantify the relationship between physiological rates across an environmental gradient and can allow for comparative assessments across different biological rates and environmental conditions (Becker \& Silbiger, 2020; Kroeker, Gaylord, et al., 2014; Schulte et al., 2011; Silbiger et al., 2019). By comparing the physiological rates of organisms across environmental gradients, it becomes possible to effectively quantify and compare the constraints, metrics, and tolerance limits of species (Hochachka \& Somero, 2002). In addition, thermal performance curves have been proposed to bridge the knowledge gap among multiple stressor interactions and aspects of global change, as they delineate the relationship between physiological rates across a range of temperatures and allow for the integration of additional abiotic factors, such as salinity, oxygen availability, and pH (Gaylord et al., 2015; Huey \& Stevenson, 1979; Schulte et al., 2011; Sinclair et al., 2016).

 Thermal performance curves represent a univariate function (dose-response relationship) that empirically quantifies how measurements of a physiological system occur in relation to varying levels of an environmental factor, from single-molecule (e.g., enzyme kinetics) to organismal-level rates (e.g., consumption rate, respiration rate, growth rate) (Figure 1.2). As temperature increases, biochemical and physiological rates increase exponentially until peaking at a species-specific optimal temperature; further increases in temperature beyond the optimum lead to rapid decreases in performance rate (also known as the Arrhenius Breakpoint; (Schulte, 2015) and eventually protein denaturation, growth inhibition, and reductions in fitness (Pörtner \& Knust, 2007; Schulte, 2015; Somero, 1995). Near the upper and lower limits of an organism’s thermal niche, where temperatures reach levels high or low enough to denature crucial metabolic enzymes, and at which locomotory activity becomes disorganized, metabolic performance gradually decreases to zero, leading to the formation of unimodal thermal performance curves (Schoolfield et al., 1981; Sharpe \& DeMichele, 1977; Somero, 1995). The dynamics described are encapsulated in the Sharpe–Schoolfield model, an extension of the Boltzmann–Arrhenius model, which extrapolates the kinetic effects of temperature on cellular processes to the organismal level, as described by \eqref{eq:sharpeschoolfieldfull}:

\begin{equation}
\label{eq:sharpeschoolfieldfull}
R(T) = \frac{R_{T_{\text{ref}}} \cdot e^{\frac{-E_a}{k_B} \left( \frac{1}{T} - \frac{1}{T_{\text{ref}}} \right)}}
{1 + e^{\frac{E_l}{k_B} \left( \frac{1}{T_l} - \frac{1}{T} \right)} + e^{\frac{E_h}{k_B} \left( \frac{1}{T_h} - \frac{1}{T} \right)}}
\end{equation}

\noindent
Wherein:
\begin{itemize}
  \item $R(T)$: Metabolic rate of a biological process as a function of temperature
  \item $R_{T_{\text{ref}}}$: Baseline metabolic rate at the reference temperature $T_{\text{ref}}$
  \item $E_a$: Activation energy in electron volts (eV)
  \item $E_l$: Low-temperature activation energy in electron volts (eV)
  \item $E_h$: High-temperature activation energy in electron volts (eV)
  \item $k_B$: Boltzmann constant, approximately $8.62 \times 10^{-5}$ eV K$^{-1}$
  \item $T$: Absolute temperature (K)
  \item $T_h$: High-temperature threshold at which $\frac{1}{2}$ of the enzymes are active
  \item $T_l$: Low-temperature threshold at which $\frac{1}{2}$ of the enzymes are active
  \item $T_{\text{ref}}$: Standardization temperature in absolute temperature (K)
\end{itemize}

 Thermal performance curves are typically left-skewed and parabolic, encompassing several metrics including, but not limited to, a thermal optimum ($T_{\text{opt}}$)—the temperature at which the maximum rate of performance is achieved—($R_{\text{max}}$), representing the maximal rate of performance, and ($T_{\text{br}}$), which denotes the thermal breadth: the range where performance spans $80\%$ of the maximal rate (Fig.~1.1). Additionally, the critical thermal minimum ($CT_{\text{min}}$) and critical thermal maximum ($CT_{\text{max}}$) values signify the upper and lower thermal thresholds that organisms can tolerate \ref{fig:tpc_conceptual_diagram} (Huey \& Kingsolver, 1989; Huey \& Stevenson, 1979; Schulte et al., 2011). The tolerance thresholds and corresponding ranges are determined by an organism’s capacity to withstand sublethal and lethal conditions via organismal-level and molecular-level responses, such as utilizing anaerobic metabolism and heat shock protein induction (Somero, 2022; Tomanek \& Somero, 2002). It has been shown that exposure to concurrent drivers of ecological change, like OA, will incur physiological costs and limit an organism’s aerobic scope, thereby reducing the breadth of performance and, consequently, thermal limits (Gaylord et al., 2015; Pörtner, 2010; Pörtner et al., 2017; Pörtner \& Farrell, 2008).
 
\newpage

```{r fig_1_2_tpc_conceptual_diagram, results='asis', echo=FALSE}
cat("
\\begin{figure}[ht]
  \\centering
  \\includegraphics[width=0.9\\textwidth]{", here::here("figures", "chapter1", "Fig_1_2_TPC_Conceptual_Diagram.png"), "}
  \\caption[Conceptual diagram of a thermal performance curve (TPC).]{Figure 1.2. Conceptual diagram of a thermal performance curve (TPC) for metabolic rates across a range of temperatures based on the Sharpe--Schoolfield model (Schoolfield et al., 1981; Sharpe \\& DeMichele, 1977). The dashed vertical line in the center indicates the thermal optimum ($T_{\\text{opt}}$), while the dashed horizontal line at the highest point of the curve denotes the highest metabolic rate ($R_{\\text{max}}$). The dotted vertical line at each end of the curve denotes the thermal limits, including the critical thermal minimum ($CT_{\\text{min}}$) and critical thermal maximum ($CT_{\\text{max}}$). The arrow parallel with the increasing slope of the curve represents the activation energy ($E_a$), while the arrow parallel with the downward slope of the curve, beyond the optimum temperature, represents the deactivation energy ($E_h$) of the curve. The thermal breadth range ($T_{\\text{br}}$) is denoted by the horizontal dotted line segment with arrows at each end spanning the length of the curve corresponding to temperatures at which the metabolic rate exceeds 80\\% of the peak performance. (Created using the rTPC package, Padfield et al., 2021.)}
  \\label{fig:tpc_conceptual_diagram}
\\end{figure}
")
```


 Employing a performance curve approach, this research delineated how OA affects the energetic demands (O$_2$ consumption) of the black turban snail, (\textit{Tegula funebralis}) across a gradient of temperature. The impact of OA is particularly significant for calcifying organisms, such as gastropods, that experience reductions in calcification rates, more so than other calcifying groups (Bellwood et al., 2004; Kroeker, Kordas, et al., 2013). As an abundant herbivore ubiquitous across intertidal ecosystems along the CCS, \textit{T. funebralis}, reaching population densities of over 1000 individuals per m$^{2}$ in the Northern West Coast of the United States, plays a crucial role in the energy flow through coastal food webs (Paine, 1971), directly affecting algal communities and serving as prey for a variety of predators (Paine, 1966, 1971, 1980). Understanding these interactive effects on herbivores is crucial, as the macroalgal-herbivore interaction is the primary pathway for energy transfer across trophic levels (O'Connor et al., 2009). \textit{T. funebralis} is also a prime subject for OW research due to its tolerance across a broad temperature range, compared to lower intertidal congeners within the genus \textit{Tegula}, which has facilitated its widespread distribution across the mid-high intertidal zone spanning from Vancouver Island, British Columbia, Canada (51$^\circ$N), to San Geronimo Island, Baja California, Mexico (30$^\circ$N) (Fawcett, 1984; Frank, 1975; Gravem \& Morgan, 2017; Morris et al., 1980; Nielsen, 2001). Furthermore, \textit{Tegula funebralis} follows the temperature-size rule (sensu Angilletta \& Dunham), exhibiting declines in body size with increasing temperatures along both latitudinal and intertidal zonation gradients, with larger individuals along the Northern regions of its distribution and smaller individuals along the Southern region of its distribution (Byers \& Mitton, 1981; Cooper \& Shanks, 2011; Frank, 1975). The outcomes of this research help reveal how changes in vital rates could affect population dynamics and, consequently, ecosystem processes in our changing oceans (Kroeker et al., 2017). Investigating the interactive effects of OA and OW is essential to enhancing our understanding of the physiological capacities of marine organisms to withstand environmental change, and thereby integral for conservation, management, and policy.
