
# Chapter 2: Ocean acidification alters thermal performance metrics and increases energetic demand in the intertidal gastropod, \textit{Tegula funebralis} {-}


## Introduction {-}

 The stability of marine ecosystems is undergoing significant changes in energy dynamics due to the escalating physiological costs imposed by a rapidly changing environment. Extractive industries have fundamentally restructured the global carbon cycle by combusting previously sequestered CO$_2$ into the atmosphere, triggering a global physicochemical shift within the oceans (Wolff et al., 2015). The ocean has served as the primary reservoir for absorbing these planetary changes, uptaking approximately a quarter of all anthropogenic-induced CO$_2$ emissions (Doney et al., 2009; Feely et al., 2004) and a thermal energy influx of approximately 10.9 Zetta Joules (Cheng et al., 2023), resulting in the dual processes of ocean acidification and warming (OA \& OW). These changes equate to a rate of change unprecedented in geological history over the past 56 million years with diminutions in pH corresponding to a 30\% increase in ocean acidity and a temperature increase energetically analogous to multiple nuclear detonations every few seconds (Burger et al., 2020; Friedlingstein et al., 2022). This stark analogy underscores the massive scale of energy redistribution within marine environments, which is altering the energetic demands of individual organisms and cascading to affect the complex network of species interactions that regulate populations and structure communities (Odum, 1968; Paine, 1980). These rapidly changing conditions force evolutionary responses of species within relatively short ecological time frames. Thus, deciphering the energetic demands imposed by concurrent changes in the abiotic environment is crucial for understanding how organisms maintain physiological homeostasis in changing environments (Somero, 2020; Somero et al., 2016). Ultimately, understanding the interactive effects of OA and OW remains an utmost priority for science, conservation, and policy.

 Ocean warming will affect virtually all marine ecological processes as changes in temperature have direct impacts on the temperature dependence of all biological and chemical processes (Brown et al., 2004; Hochachka \& Somero, 2002; Hofmann \& Todgham, 2010; Huey \& Stevenson, 1979; Levins, 1968; Schmidt-Nielsen, 1997; Somero, 2002). These impacts will increase the kinetic speed of biochemical reactions, modify internal acid-base regulation (variations in pH $\sim$ 0.017 per $^\circ$C of body temperature change), modulate metabolic pathways, and shift the equillibria of constructing biological structures (Pörtner, 2012a; Somero et al., 2016). Through doing so, changes in temperature ultimately impact energetic demands and thus the fitness and distribution patterns of marine species (Huey \& Kingsolver, 1989). In ectothermic species, cellular respiration is governed by the ability to withstand temperature, with eurythermal species capable of surviving across a wide range of temperatures, or stenothermal, restricted to a narrow temperature range. For example, temperature changes differentially affect the metabolic demands of intertidal gastropods in the genus \textit{Tegula}, with the species \textit{T. funebralis} situated within the high-mid intertidal zone experiencing higher metabolic rates due to their greater tolerance across a range of temperatures, compared to subtidal congeners \textit{T. brunnea} and \textit{T. montereyi}, which experience relatively less temperature variability and lower thermal tolerances (Byers \& Mitton, 1981; Frank, 1975; Somero, 2011; Tomanek \& Somero, 1999).

 Ocean acidification will also interact against a backdrop of warming to affect the metabolic activity of marine organisms, posing a unique threat to marine calcifiers and potentially elevating the energetic costs associated with metabolic activity. Similar to temperature increases, changing acidity will influence the internal acid-base concentration gradients, exerting energetic costs on maintaining cellular homeostasis (Bozinovic \& Pörtner, 2015; Michaelidis et al., 2005b; Somero, 2020). Moreover, changes in seawater carbonate chemistry elevate the energetic costs associated with calcification and possibly undermine the formation of calcified structures within marine organisms (Mekkes et al., 2021; Spalding et al., 2017), yet, in contrast, some marine calcifiers may be able to maintain or even elevate calcification in response to OA (e.g., calcite versus aragonite, see Barclay et al., 2019). For example, gastropods like \textit{Tegula funebralis} and \textit{Nucella ostrina} show cryptic variability in calcification under ocean acidification, with \textit{T. funebralis} experiencing significant shell integrity reduction, while \textit{N. ostrina} remains relatively unaffected, indicating species-specific responses to energetic demands (Barclay et al., 2019; Gaylord et al., 2019).

 The dual pressures of OA and OW pose significant challenges for coastal marine organisms in highly stochastic physical environments, often facing natural variability that exceeds future projections (Helmuth, 1999; Jellison et al., 2016; K. Wolfe et al., 2020). The California Current System provides a living laboratory of climatic changes that allows us to understand how organisms thrive and persist amidst the inherent variability in seawater carbonate chemistry and temperature (Hofmann et al., 2014; Gaylord et al., 2014; Somero et al., 2016). Intertidal organisms, for example, experience significant temperature changes, as high as 25$^\circ$C within a single tidal cycle, with Southern California intertidal ecosystems displaying aerial and aquatic temperatures ranging from 12.2 to 45.05$^\circ$C (Davis, 2001; Helmuth et al., 2016; Helmuth, 1998; Tomanek \& Somero, 1999; K. Wolfe et al., 2020). Additionally, diurnal variations in the carbonate chemistry of intertidal rock pools, which become isolated at low tide, can cause significant pH fluctuations of up to $\sim\!1.11\ \mathrm{pH}_\mathrm{T}$ units within a single tide cycle (Jellison et al., 2016, 2022; Kunze et al., 2021; Kwiatkowski et al., 2016; Silbiger \& Sorte, 2018). Community-level metabolic activity adds to this variability during conditions when CO$_2$ accumulation from respiration surpasses photosynthetic activity, leading to further reductions in pH throughout nighttime dissolution lows and biophysical feedback loops (Fields \& Silbiger, 2022; Gaylord et al., 2019; Kwiatkowski et al., 2016; Silbiger \& Sorte, 2018). Thus, intertidal ecosystems exhibit drastic variability that offer a glimpse into the future, providing insights on how organisms respond to changing environments.

 A key goal of ecology is to uncover patterns and mechanisms within ecological communities (Levins, 1992). One of these objectives is to determine whether the combined effects of multiple stressors will act interactively through additive, synergistic, or antagonistic interactions—and of prime importance is whether concurrent global changes (such as OA and OW) will overlay to amplify environmental change (Côté et al., 2016; Darling \& Côté, 2008). Thermal performance curves (TPCs) have been suggested to fill this gap of uncertainty, as they empirically characterize the relationship between biological rates of performance across a gradient of temperatures (Angilletta, 2009; Levins, 1969; Schulte et al., 2011). Additionally, TPCs facilitate the integration of various abiotic factors, enabling comparative physiological metrics, such as metabolic rates and thermal tolerances, between populations and species. This integration serves as a “crystal ball” (sensu Somero, 2011) for predicting the impacts of global change (Dowd et al., 2015; Silbiger et al., 2019; Sinclair et al., 2016). The Metabolic Theory of Ecology (MTE) provides a mechanistic framework for integrating TPCs to changes in energetic expenditure, interlinking ecological drivers and organismal metabolism, and positing that metabolic rates are governed by temperature-dependent enzyme reaction rates, the size of the organism, and the stoichiometry of an organism’s biochemical processes (Brown et al., 2004; Gillooly et al., 2001). Organism-level aerobic respiration (O$_2$ consumption) provides a direct measure of metabolic rate and serves as a proxy for cellular respiration because oxygen is essential for the production of ATP through oxidative phosphorylation, thus allowing us to estimate the energetic expenditure of marine organisms. By analyzing respiration rates through a TPC approach, I can delineate the relationship between temperature and metabolic demand alongside the comparative assessment of additional abiotic factors of global change such as OA.

 For this study, I investigated physiological energetics of the black turban snail \textit{Tegula funebralis}, a eurythermal intertidal gastropod situated within the thermally stressful high intertidal zone of the Pacific Northwest, United States ($-0.5$ m to 1.5 m, Tomanek \& Somero, 1999), to explore the interactive effects of ocean acidification on respiration rates across a gradient of temperature in a controlled laboratory setting. \textit{T. funebralis}, distributed along the west coast of North America from Canada (51$^\circ$N) to Mexico (30$^\circ$N) (Morris et al., 1980), was selected to implore this question because of its ubiquity across intertidal ecosystems (ranging in densities of up to $>1000~individuals~per~m^2$ in the northern distribution and ranging from 10--100 individuals per m$^2$ in the southern distribution (Jones \& Long, 2018; Pacific Rocky Intertidal Monitoring, 2023; Paine, 1971)), its important role as a macroalgal herbivore/detritivore in influencing energetic flow within intertidal food webs (up to 60\% energy transfer from primary producers to primary consumers, see Paine, 1969; Paine, 1971), observed body size declines associated with increasing temperatures over the past few decades, consistent with the temperature-size rule (Elahi et al., 2020), and its particular vulnerability to calcification reductions and anti-predator behavioral impairment due to OA (Barclay et al., 2019; Jellison et al., 2016). 

 Within this research, I posed the question: how does exposure to decreased pH influence thermal performance and energetic expenditure of the intertidal gastropod, \textit{Tegula funebralis}? I hypothesized that the thermal optimum ($T_{\text{opt}}$) and critical thermal maximum ($CT_{\text{max}}$) for respiration rates will shift towards lower temperatures, indicating a reduced ability to sustain optimal metabolic activity in the face of ocean acidification (Figure~\ref{fig:tpc_hypothesis_schematic}). Additionally, I expect a decrease in the thermal breadth of the curve ($T_{\text{br}}$), indicating a narrower range of temperatures at which the gastropod can effectively maintain respiratory rates (Figure~\ref{fig:tpc_hypothesis_schematic}). Consequently, I anticipate that \textit{Tegula funebralis} will exhibit increased energetic expenditure as a function of rising sea temperatures and lowered pH levels, with more pronounced changes at temperature extremes, thereby reflecting a higher cost of maintaining homeostasis under elevated stress. Predicting the consequences of concurrent global changes using a thermal performance curve approach will enable me to make generalized hypotheses regarding how ocean acidification may impact organismal-level processes and infer how these changes will scale up to affect ecosystem function (e.g., net primary productivity, calcification, etc.).

\newpage

```{r fig_2_1_latex, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=0.9\\textwidth]{", here::here("figures", "chapter2", "Fig_2_1_TPC_Hypothesis_Schematic.png"), "}
  \\caption[Hypothesis schematic diagram of TPCs under ambient and low pH conditions.]{Hypothesis schematic diagrams of TPCs for respiration rates across a range of temperatures with exposure to either ambient or low pH conditions based on the Sharpe--Schoolfield model (Schoolfield et al., 1981; Sharpe \\& DeMichele, 1977). The dashed vertical lines indicate the optimal temperatures ($T_{\\text{opt}}$) for each curve, with a reduction in the thermal optimum at decreased pH, while the dotted vertical lines denote the thermal limits, including the minimum critical temperature ($CT_{\\text{min}}$) and maximum critical temperature ($CT_{\\text{max}}$), with constrictions hypothesized at lower pH. The arrow pointing upwards (parallel with the increasing slope of the curve) represents the activation energy ($E_a$) and predicts an increased activation energy under decreased pH, while the arrow pointing downwards (past the optimum) represents a steeper deactivation energy ($E_h$) with exposure to decreased pH. The dashed horizontal arrow denotes the highest metabolic rate ($R_{\\text{max}}$) with a hypothesized increase in energetic requirements (respiration rate $\\sim$ O$_2$ consumption) under decreased pH. The thermal breadth range ($T_{\\text{br}}$, 80\\% of peak performance) is denoted by the horizontal dotted line segment with arrows at each end and hypothesized to constrict in range throughout exposure to decreased pH.}
  \\label{fig:tpc_hypothesis_schematic}
\\end{figure}
")
```

## Methods {-}

### Experimental Design {-} 

 Using a mesocosm system, I exposed \textit{Tegula} to one of eight temperature treatments [ranging from 12$^\circ$C to 26$^\circ$C at 2$^\circ$C intervals; $n=8$] and to one of two pH treatments [7.9 pH$_\mathrm{T}$ (ambient); 7.7 pH$_\mathrm{T}$ (low); $n=2$], resulting in sixteen temperature by pH combinations ($n=4$ \textit{Tegula} per treatment). After a 7-day tank adjustment period and a 10-day exposure to experimental treatments, respiration rates were measured for each individual snail ($n=60$). Furthermore, rates of oxygen consumption were converted to J g$^{-1}$ h$^{-1}$ to translate metabolic changes to changes in energetic requirements.

 Temperature (12--26$^\circ$C) and pH$_\mathrm{T}$ (7.7 and 7.9) ranges were chosen to mirror the local variability that \textit{Tegula} experience within intertidal ecosystems of the Southern California Bight. Data from a subtidal monitoring station in Newport Beach, CA, showed seawater temperatures ranging from 11.7$^\circ$C to 25.2$^\circ$C over the past three years (Carter, 2022), with an average of 21$^\circ$C during the summer months (August--September) when my study was conducted (Fig.~3B, Appendix 1A). Moreover, offshore pH$_\mathrm{T}$ recorded at a subtidal shore station in Newport Beach, CA revealed a mean pH$_\mathrm{T}$ of 8.01 $\pm$ 0.07, with minima reaching 7.3 (Figure~\ref{fig:study_site_map}, Appendix B1). Previous research has shown tidepool pH$_\mathrm{T}$ variability within the Southern California Bight to range from approximately 7.5 to 8.7 over a diel cycle compared to adjacent ocean diel variability ranging from 7.9 to 8.3 (Silbiger and Sorte, 2018), highlighting the relevance of the chosen pH$_\mathrm{T}$ levels 7.7 and 7.9.


### Species Collection and Adjustment {-} 

 Black turban snails ($n=45$) were collected haphazardly from tidepools in Point Fermin, San Pedro, CA (Figure~\ref{fig:study_site_map}) in August 2022 (under permit CDFW SCPID: S-220520002-22054-001) at low tide. Upon collection, each snail was measured for shell width ($\pm$ 0.001 mm) using Vernier calipers. To minimize variability resulting from mass-specific metabolic rate, only individuals ranging from 19--24 mm in shell width ($>18 mm$ mature individuals $\sim$ 10 years old; Paine, 1971) were selected for the experiment. Organisms were transported to California State University, Northridge, in a wet insulated container. Snails were weighed for blotted wet mass (g) using an electronic balance to the nearest 0.0001 g, measured for volume (mL) using volumetric displacement, and tagged for identification using a FloyTag placed at the apex of the dorsal side of the shell with CorAffix\textsuperscript{\textregistered} cyanoacrylate adhesive.


```{r fig_2_2_study_site_map, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=6.25in]{", here::here("figures", "chapter2", "Fig_2_2_Study_Site_Map.png"), "}
  \\caption[Study site location map and associated SST and pH\\textsubscript{T} variability.]{Study site location map and associated temporal variability within sea surface temperature (SST) and pH\\textsubscript{T} at a nearby shore station (Newport Beach, CA). (A) Annotated map of the Pacific Coast with an inset zooming into the study site at Point Fermin State Beach, California (33.7056$^\\circ$N, 118.2935$^\\circ$W), created in R using \\texttt{raster}, \\texttt{sf}, \\texttt{ggmap}, and \\texttt{ggmapinset} (Hijmans et al., 2015; Kahle \\& Wickham, 2013; Pebesma, 2018; Suster, 2023). (B) Violin plot showing the monthly frequency distribution of daily average SST data spanning 2020 to 2023 from Newport Beach, CA at a nearby shore station approximately $\\approx$ 23 km from the study site. Horizontal dashed lines indicate experimental temperature treatments ranging from 12$^\\circ$C--26$^\\circ$C by 2$^\\circ$C increments. (C) Analogously, the violin plot for seawater pH\\textsubscript{T} showcases the monthly frequency distribution of daily average values on the total scale, spanning 2020 to 2023 at the same shore station. The horizontal dashed lines highlight the experimental treatment levels (pH\\textsubscript{T} 7.9 (ambient) and 7.7 (low)). Data for these plots were provided by the Southern California Coastal Ocean Observing System and the Shore Stations Program at the Scripps Institution of Oceanography, supported by the California Department of Parks and Recreation, Natural Resources Division, Award \\#C1670003.}
  \\label{fig:study_site_map}
\\end{figure}
")
```

 Each black turban snail was randomized and assigned to one of 16 experimental aquaria, with four individuals per aquarium. All aquaria were set to measured seawater temperature and seawater pH from the time of collection in order for the snails to adjust to tank conditions. Temperature was set to 16$^\circ$C and pH$_\mathrm{T}$ was set to 7.9. The next day, snails were moved to a pH$_\mathrm{T}$ treatment of either 7.9 or 7.7. On the second day in the mesocosm system, snails slated for temperature conditions either higher or lower than 16$^\circ$C were increased or decreased at a gradual temperature change of 2$^\circ$C day$^{-1}$ such that all snails reached their treatment temperature and pH after seven days. Throughout the adjustment and the subsequent experimental period, all snails were fed a three-inch in diameter circle of fresh giant kelp (\textit{Macrocystis pyrifera}) from nearshore Point Fermin, a highly preferred food (Steinberg, 1985) every three days. This feeding rate was chosen to maintain nutritional consistency of algae and prevent metabolic rate fluctuations due to food availability (Brockington, 2001).

### Mesocosm Settings Overview and Maintenance {-}

This experiment was conducted in a closed-loop mesocosm system at California State University, Northridge, using natural seawater collected from the Southern California Marine Institute (SCMI) in San Pedro, CA, and filtered through three filters (20~$\mu$m, 5~$\mu$m, and a carbon filter [up to 1~$\mu$m]) prior to being introduced into the sump of the mesocosm system. The mesocosm was equipped with experimental tanks (53.9~cm (L) $\times$ 31.75~cm (W) $\times$ 34.29~cm (H)) each with individual controls for pH, temperature, light intensity, and water flow. Each aquarium was outfitted with a submersible powerhead pump (Hydor Nano Koralina 240 powerhead, 240 GPH), a 200 or 400W heater (Hydor aquarium heater), a temperature probe (Neptune Systems, $\pm 0.1^\circ$C), a pH probe (Neptune Systems, Lab Grade Double Junction, measures pH from $4.0 to 12.0 \pm 0.1$), three flow sensors (Apex, FS-25 ¼" fitting, flow rates from 3--12 GPH (12--24 LPH)), and a continuous temperature logger (HOBO TidBit MX2203, $\pm 0.2^\circ$C ). LED lights (Halo Basic M-110) in each tank followed a diurnal light cycle to mimic light levels between local sunrise and sunset conditions. Individual aquaria were programmed to simulate the semi-diurnal tidal patterns that characterize the West Coast of the United States, undergoing two high and two low tide fluctuations within a 24-hour cycle, each lasting six hours, by programming inflow and outflow solenoid valves (Apex Neptune). Flow rates were measured on a daily basis using a graduated cylinder and timer to ensure an inflow of 10~L~h$^{-1}$, constant total inflow of 10~L~h$^{-1}$, and a constant outflow drain rate of 15~L~h$^{-1}$, thereby creating the desired tidal effect and mimicking the biological rhythmicity these organisms would experience in the field.

 Temperature and pH were controlled by a stat system using Apex programmable aquaria controllers outfitted with pH and temperature probes (Neptune Systems). Tank temperature was controlled with aquarium heaters while pH levels were regulated through the direct bubbling and mixing of CO$_2$, facilitated by solenoid valves attached to a CO$_2$ cylinder. Additionally, a venturi connected to a pump facilitated the mixing of ambient air to stabilize the pH levels in the treatment tanks. Recirculating seawater in the closed-loop system underwent a series of biological and chemical filtration in the central holding reservoir, throughout which seawater was chilled to a temperature of 10$^\circ$C (Aqua Logic Delta Star, DS-4 chiller) and bubbled with CO$_2$-free air from a Phosban reactor (Phosban 150 Reactor), forcing CO$_2$ to be off-gassed and returning pH back to ambient conditions prior to recirculating into treatment tanks. Additionally, the recirculating seawater was purified using three 50~$\mu$m carbon bag filters, eight mesh filters, and an ultraviolet sterilizer (Comet Series 95 Watt Lamp). Weekly water replacements, accounting for approximately 50\% of the total volume, were conducted to prevent the accumulation of metabolic waste and to maintain stable carbonate parameters within the system.

### Measurements to Monitor Experimental Seawater Conditions {-}

 In addition to the apex-measured pH and temperature conditions, water quality parameters were measured to monitor environmental conditions within the tanks. pH and temperature were measured daily at approximately 9:30 AM to facilitate the calibration of in-tank temperature and pH probes. Discrete temperature readings were acquired using a Thermo Fisher Trace digital thermometer with an accuracy of $\pm~0.05^\circ$C, providing measurements to the nearest $0.001^\circ$C. In tandem, a Thermo Scientific Orion Star A325 pH/Conductivity Portable Meter was employed to measure millivolts (used to calculate pH) and an Orion Star probe employed to measure salinity with respective precisions of 0.1 for mV (accuracy, $\pm~0.05\%$) and 0.01 ppt for salinity ($\pm~0.05\%$). Dissolved oxygen (DO) levels were monitored using the YSI Pro2030 multiparameter probe, which provided measurements in both \% saturation and mg~L$^{-1}$, with a precision of $0.01~mg~L^{-1}$ and $0.1\%$ (accuracy, $\pm 0.2~mg~L^{-1}$ or $\pm~2\%$, respectively). The pH$_\mathrm{T}$ values for individual aquaria were calculated using the \texttt{seacarb} package in R, which accounted for the measured mV values from a Tris calibrated probe, temperature from the trace digital thermometer, and sample salinity in accordance with the Dickson Protocol SOP 6a. Total Alkalinity (TA) samples were collected once every 3--4 days from each experimental tank and sump and stored in triple-rinsed, acid-washed 125~mL Nalgene containers. The collected samples were analyzed within 24 hours of collection using a T-5 automatic titrator (Mettler Toledo), following the potentiometric titration protocol (SOP3a) for best practices in ocean CO$_2$ measurements. To verify accuracy, a certified reference material (Reference Material for Oceanic CO$_2$ Measurements, A. Dickson, Scripps Institution of Oceanography) was run prior to each total alkalinity measurement with an error $\leq0.85\%$ off from the certified value.

Total alkalinity and pH$_\mathrm{T}$, along with \textit{in situ} temperature and salinity, were used to calculate the remaining carbonate system parameters (pCO$_2$, fCO$_2$, HCO$_3^-$, CO$_3^{2-}$, DIC, $\Omega$ aragonite, and $\Omega$ calcite) by solving the Thermodynamic Equation of Seawater for the known pair of carbonate parameters (TA \& pH$_\mathrm{T}$), using the K$_1$ dissociation constant of $10^{-6.0}$ and K$_2$ dissociation constant of $10^{-9.0}$ from Lueker et al.\ (2000), K$_f$ of $10^{-5.4}$ from Perez and Fraga (1987), and K$_s$ of $10^{-1.0}$ from Dickson (1990) using the \texttt{seacarb} package in R; resulting in the relative uncertainties of $uc[\text{CO}_2^*]/[\text{CO}_2^*] = 2.6\%$ and $uc[\text{HCO}_3^-]/[\text{HCO}_3^-] = 3.6\%$ for the known pair.

### Measuring Snail Respiration Rates {-}

 Organic biomass-normalized respiration rates were measured at the conclusion of the experiment. Prior to conducting respirometry, each individual snail shell was thoroughly scrubbed using an acrylic brush to remove any epibionts that could potentially obscure respiration rates. Respirometry trials were conducted in the dark to avoid the effects of microbial photosynthetic activity on seawater chemistry. Snail respiration rates were assessed by measuring oxygen consumption within sealed, water-tight acrylic chambers (650~mL) for 45 minutes. Vexar plastic mesh wire separated the snail from a magnetic stir bar ($200~rpm~s^{-1}$) placed at the bottom of the chamber to prevent oxygen stratification. During the respirometry trials, temperature was stabilized using an insulated cooler and a programmable thermostat system (Apex Controller, Neptune Systems, $\pm~0.1~^\circ$C) connected to a submersible water heater (Finnex 300W Titanium Heater) and chiller (Aqua Logic Delta Star). pH was regulated using aquaria in the mesocosm system as described above and chambers were filled with water at a pH of either 7.7 or 7.9 depending on the snail’s treatment conditions. Temperature measurements were taken continuously ($\pm~0.1~^\circ$C) throughout the trials using temperature probes (Thermo Scientific Traceable Thermometer; $\pm~0.05~^\circ$C), and oxygen measurements were taken at a frequency of 1~Hz using a Presens fiber optic oxygen dipping probe (DP-PSt8) and continuously monitored throughout the respirometry trial using Presens Software. To account for differences in background oxygen fluctuations, oxygen consumption was also measured in a blank seawater control for every temperature and pH combination.

 After the respirometry trials, snails were euthanized by freezing. Afterwards, body tissue was removed from each gastropod, and dry weight was measured after drying the sample at $60^\circ$C for 48 hours. Subsequently, after ensuring the weights remained constant, ash-free dry weight (the organic fraction of organism biomass) was measured after burning the sample at $450^\circ$C for 4 hours.The calculation of organic biomass via ash-free dry weight (AFDW) was determined using the following equation:

\begin{equation}
\label{eq:afdw}
\mathrm{AFDW} = \mathrm{SFDW} - \mathrm{AW}
\end{equation}

Wherein, AFDW is ash-free dry weight of the sample (g), SFDW is the shell free dry weight of the sample (g), and AW = Ash weight content of the sample (g).

 To calculate respiration rates for each individual, oxygen evolution over time within each chamber was thinned to every 20 seconds, and respiration rates were calculated using repeated local linear regressions with the package \texttt{LoLinR}. Organismal respiration rates were standardized to the volume of water within the chamber. Seawater oxygen fluctuations from blank control chambers were subtracted from respiration rates as a control, and the oxygen consumption rate of each individual organism ($\mu$mol O$_2$ g$^{-1}$ h$^{-1}$) was calculated by normalizing respiration rates to organic biomass.

### Measuring Snail Respiration Rates {-}

 Given that cellular respiration involves the consumption of oxygen (O$_2$) through respiratory activity to produce energy in the form of adenosine triphosphate (ATP) (1), respiratory rates can be translated to energetic expenditure. Energy expenditure was calculated from respiration oxy-joulimetric conversions for the energetic equivalents of respiratory oxygen consumption (Table~\ref{tab:oxygen_consumption_table}), translating metabolic rates into energy currency (Joules).
To calculate energy expenditure (J), oxygen consumption rates in $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ were converted to mmol O$_2$ g$^{-1}$ h$^{-1}$ and were then translated to J g$^{-1}$ h$^{-1}$ using an average value of oxy-enthalpic equivalents across biomolecules (including lipid, protein, and carbohydrates, which averaged: 460~J~mmol$^{-1}$ O$_2$). Energetic and biochemical equivalents are derived from the theoretically calculated enthalpy change of oxidative catabolic reactions per unit of oxygen consumed, $\Delta_k$HO$_2$, ranging from $-430$ to $-480$~kJ~mol$^{-1}$ O$_2$.

\begin{table}[H]
\captionsetup{width=\textwidth}
\centering
\caption[Energetic and biochemical equivalents of respiratory oxygen consumption.]{Energetic and biochemical equivalents of respiratory oxygen consumption (O$_2$), based on metabolic oxidation of carbohydrates, lipids, and proteins. Units are expressed per gram, liter, and mole of O$_2$, and averaged across biomolecules. (Adapted from Elliott \& Davison, 1975; Gnaiger, 1983a; Gnaiger \& Kemp, 1990.)}
\vspace{0.5em}
\begin{tabular}{lccc}
\toprule
\textbf{Biomolecule} & \textbf{kJ g$^{-1}$ O$_2$} & \textbf{kJ L$^{-1}$ O$_2$} & \textbf{kJ mol$^{-1}$ O$_2$} \\
\midrule
Carbohydrate         & 14.77                     & 21.06                      & 447.93                       \\
Lipid                & 19.58                     & 19.41                      & 481.86                       \\
Protein              & 13.61                     & 14.10                      & 444.01                       \\
\textbf{Average}     & \textbf{15.99}            & \textbf{18.86}             & \textbf{457.93}              \\
\bottomrule
\end{tabular}
\label{tab:oxygen_consumption_table}
\end{table}

### Statistical and Data Analysis {-}

Continuous temperature measurements from HOBO loggers within each individual tank were summarized to hourly rates and compared between treatments throughout the experimental period. To assess that our temperature treatments were statistically different from one another, a two-way Analysis of Variance (ANOVA) was conducted on the temperature treatments, accounting for any potential interactions between pH treatments. A Tukey-Kramer post-hoc test was applied to test for pairwise interactions. Additionally, a Welch Two Sample $t$-test was used to test for differences in pH$_\mathrm{T}$ by pH treatment and Cohen's $d$ was calculated to measure the effect size of the difference between the pH treatments (Patil, 2021; Welch, 1947).

 Individual thermal performance curves (TPCs) were used to investigate the relationship between temperature and respiration rates of \textit{Tegula funebralis} for each pH treatment. Only organisms that faced mortality or issues with respiration rate measurements (e.g., probe failure during respirometry trial) were excluded from analysis (2 snails had probe failure (16 \& 12: Ambient) and 2 faced mortality (24: Ambient; 26: Low)). A nonlinear regression model fitting pipeline was applied to model thermal performance curves across five models suitable for ectotherm physiology (Boatman, Gaussian, Shape-Schoolfield Full-Temperature Inactivation, Sharpe-Schoolfield High-Temperature Inactivation, Weibull) using the \texttt{rTPC} package (Padfield, O’Sullivan, \& Pawar, 2021). Nonlinear models were fitted using the \texttt{nls.multstart} package, which utilizes the nonlinear least squares (NLS) method calculated with the Levenberg–Marquardt algorithm to avoid convergence to local minima (Moré, 1978; Padfield \& Matheson, 2023). Diagnostic plots were employed to assess the normality of residuals for TPCs and identify any potential outliers or systematic patterns within the data. AIC values for the model fits were extracted using the \texttt{MuMin} package, and the model with the lowest Akaike Information Criterion corrected for small sample sizes (AICc) was used for inference (Bartoń, 2023). The corrected Akaike Information Criterion (AICc) is a modification of the Akaike Information Criterion (AIC) that provides an adjustment for small sample sizes and is defined as $AIC_c = AIC + \left( \frac{n - k - 1}{2k(k+1)} \right)$ where $n$ is the sample size and $k$ is the number of estimated parameters in the model (Akaike, 1974). The Sharpe--Schoolfield high activation energy model, chosen due to its goodness of fit and physiological relevance to ectotherms based on enzyme kinetics (Schoolfield et al., 1981), is described by the following equation:

\begin{equation}
R(T) = \frac{R_{\text{Tref}} \cdot e^{\left( -\frac{E_a}{k_B} \left( \frac{1}{T} - \frac{1}{T_{\text{ref}}} \right) \right)}}{1 + e^{\left( \frac{E_h}{k_B} \left( \frac{1}{T_h} - \frac{1}{T} \right) \right)}}
\label{eq:sharpe_schoolfield}
\end{equation}

 where $R(T)$ is the metabolic rate as a function of temperature, $R_{\text{Tref}}$ is the baseline metabolic rate at the reference temperature $T_{\text{ref}}$, $E_a$ is the activation energy in electron volts (eV), $E_h$ is the high-temperature deactivation energy in electron volts (eV), $k_B$ is the Boltzmann constant in eV/K, $T$ is the temperature in Kelvin, $T_h$ is the high temperature thresholds at which half the enzymes are active, and $T_{\text{ref}}$ is the standardization temperature.

 After model selection, bootstrap resampling with 1000 iterations ($R=1000$) was employed to obtain estimates, and the bias-corrected and accelerated (BCa) method was used to calculate the confidence intervals using the \texttt{car} package (Fox \& Weisberg, 2018). The thermal performance metrics were extracted from the model using residual resampling to assess parameter uncertainty with 95\% confidence intervals for $E_a$ and $E_h$, as well as variables calculated from the model parameters, including thermal optimum ($T_{\text{opt}}$), thermal breadth ($T_{\text{br}}$), maximum rate of performance ($R_{\text{max}}$), and critical thermal maximum ($CT_{\text{max}}$). The thermal optimum ($T_{\text{opt}}$) was estimated by restructuring the Sharpe-Schoolfield equation to solve for the temperature at which the derivative of the metabolic rate with respect to temperature was equivalent to zero (peak of the curve, $dR/dT = 0$), resulting in the following equation:

\begin{equation}
T_{\text{opt}} = \frac{E_h \cdot T_h}{E_h + k_B \cdot T_h \cdot \ln\left( \frac{E_h}{E_a} - 1 \right)}
\label{eq:topt}
\end{equation}

 Differences between the parameters extracted from TPCs for each pH treatment were tested using the bootstrapped parameters, considering parameters with 95\% confidence intervals that did not overlap as statistically different from one another. Calculated $T_{\text{opt}}$ values and current and predicted changes in sea surface temperature data (+2$^\circ$C and +4$^\circ$C above current) for the nearest shore station at Newport Beach, CA were used to extrapolate the number of days that \textit{Tegula funebralis} experiences temperatures beyond its thermal optima. Additionally, the $Q_{10}$ coefficient (thermal sensitivity quotient, which describes the change in metabolic rate over a 10$^\circ$C change in temperature) was estimated by calculating the magnitude of change in metabolic rates resulting from a 10$^\circ$C change in temperature ($\Delta T = 10^\circ$C) using the \texttt{respirometry} package. The following equation was used (Birk et al., 2018; Gillooly et al., 2001; Mundim et al., 2020):

\begin{equation}
Q_{10} = \left( \frac{R_2}{R_1} \right)^{\frac{10}{T_2 - T_1}}
\label{eq:q10}
\end{equation}

where $R_1$ and $R_2$ are the metabolic rates at temperatures $T_1$ and $T_2$ respectively.

 To test for differences in energy expenditure, measured in Joules per gram of ash-free dry weight per hour (J$\cdot$g$^{-1}$$\cdot$h$^{-1}$), between the various temperature and pH treatments, a two-way ANOVA was conducted. Values were log-transformed to meet the assumption of normality before statistical tests were performed. Following the two-way ANOVA, pairwise comparisons of energetic expenditure between pH treatments within each temperature treatment were performed using estimated marginal means with a Bonferroni correction for multiple comparisons using the \texttt{emmeans} package in R (Lenth, 2016).

 All statistical analyses were run in the R environment, R version 4.3.2 (R Core Team, 2023). Assumptions for all parametric model’s data were visually and statistically checked prior to interpreting running statistical tests using the \texttt{performance} package (Lüdecke et al., 2021). The Shapiro-Wilk test was used to ensure the normality of the residuals data, while Levene's test was used to validate the homogeneity of variances, confirming the appropriateness of parametric analyses prior to running statistical tests (Levene, 1961; Shapiro \& Wilk, 1965).

## Results{-}

### Temperature and pH Differed Among Treatments {-}

```{r fig_2_3_mesocosm_tank_treatments, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=5in]{", here::here("figures", "chapter2", "Fig_2_3_Mesocosm_Tank_Treatments.png"), "}
  \\caption[Mesocosm mean seawater temperature and pH\\textsubscript{T} across temperature and pH treatments.]{Mesocosm mean seawater temperature ($^\\circ$C) and pH\\textsubscript{T} between different temperature treatments (12$^\\circ$C to 26$^\\circ$C) and levels between ambient and low pH treatments throughout the experimental duration. (A) Mean seawater temperature ($^\\circ$C) across different temperature treatments (12$^\\circ$C to 26$^\\circ$C) for ambient and low pH treatments throughout the experimental duration. Colored points represent mean temperatures (orange for ambient pH treatment, cyan for low pH treatment), with error bars showing 95\\% confidence intervals. Horizontal dashed lines indicate set temperature treatments, color-coded from light yellow (12$^\\circ$C) to dark red (26$^\\circ$C). (B) Violin plot depicting the distribution of pH\\textsubscript{T} values between ambient and low pH treatments. The internal boxplot within the violin plot shows the median, interquartile range, and whiskers extending to 1.5 times the interquartile range.}
  \\label{fig:mesocosm_tank_treatments}
\\end{figure}
")
```


\newpage

### Elevated Respiration Rates in Response to Temperature Contrasted Between pH Levels {-}

 Respiration rates varied significantly across temperature and pH treatments, with both pH treatments having minima at approximately 12$^\circ$C and maxima at 24$^\circ$C, with higher rates generally observed under low pH conditions. For ambient pH treatment, the mean respiration rates ranged from 14.08 $\pm$ 4.56 $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ at 12$^\circ$C to 53.82 $\pm$ 7.83 $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ at 24$^\circ$C. For low pH treatment, the mean rates ranged from 11.93 $\pm$ 0.68 $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ at 12$^\circ$C to 79.47 $\pm$ 9.21 $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ at 24$^\circ$C.

```{r fig_2_4_tpc_comparativ, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=5in]{", here::here("figures", "chapter2", "Fig_2_4_TPC_Comparative.png"), "}
  \\caption[Comparative thermal performance curves for ambient and low pH treatments.]{Comparative thermal performance curves fitted with the Sharpe--Schoolfield high-activation model for respiration rates ($\\mu$mol O$_2$ g$^{-1}$ h$^{-1}$) of *Tegula funebralis* across temperature treatments (12$^\\circ$C to 26$^\\circ$C) under (a) ambient and (b) low pH conditions. Solid lines represent model predictions, while shaded areas represent 95\\% confidence intervals based on bootstrap analysis. Each point represents the respiration rate of an individual snail (ambient pH: $n=29$; low pH: $n=31$).}
  \\label{fig:tpc_comparative}
\\end{figure}
")
```

 Comparative thermal performance curves revealed statistically significant differences in respiration rates ($R_{\text{max}}$) between ambient and low pH treatments. The $R_{\text{max}}$ was 49.6\% higher in the low pH treatment at 80.74 $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ (95\% CI = [71.85, 92.36]) compared to the ambient pH treatment, which had an $R_{\text{max}}$ of 53.88 $\mu$mol O$_2$ g$^{-1}$ h$^{-1}$ (95\% CI = [44.90, 62.77]). Other thermal performance metrics, including the optimal temperature ($T_{\text{opt}}$), thermal breadth ($T_{\text{br}}$), and critical thermal maxima ($CT_{\text{max}}$), were not statistically different between the pH treatments. The $T_{\text{opt}}$ for metabolic activity was equivalent between the low pH treatment (24.49$^\circ$C, 95\% CI = [23.68, 24.88]) and ambient pH treatment (24.63$^\circ$C, 95\% CI = [23.30, 25.17]). The thermal breadth was slightly narrower in the low pH treatment (2.89, 95\% CI = [2.47, 3.32]) compared to the ambient treatment (4.26, 95\% CI = [3.20, 6.65]), suggesting a reduced range of temperatures over which organisms maintain optimal performance under low pH conditions. The $CT_{\text{max}}$, denoting the upper thermal limit the organisms can tolerate, was found to be 27.16$^\circ$C (95\% CI = [26.70, 28.40]) in the low pH treatment and 28.32$^\circ$C (95\% CI = [27.40, 36.46]) in the ambient pH treatment. Calculations of thermal sensitivity quotients revealed the $Q_{10}$ value was higher in the low pH treatment (2.55) compared to the ambient pH treatment (2.06), with an overall $Q_{10}$ of 2.29.

```{r fig_2_5_latex, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=5in]{", here::here("figures", "chapter2", "Fig_2_5_TPC_Parameter_Estimates.png"), "}
  \\caption[Comparative thermal performance metrics between ambient and low pH treatments.]{Comparative thermal performance metrics between ambient and low pH treatments. Extracted TPC parameter estimates for the Sharpe--Schoolfield High model (high-activation) under two pH treatments (ambient and low), with accompanying bootstrapped 95\\% confidence intervals. Parameters include activation energy ($E_a$), deactivation energy ($E_h$), thermal breadth ($T_{\\text{br}}$), maximum rate of performance ($R_{\\text{max}}$), thermal optimum ($T_{\\text{opt}}$), and thermal maximum ($CT_{\\text{max}}$). Points denote mean parameter estimates, vertical lines represent the 95\\% bootstrapped confidence intervals, and asterisks (*) indicate significant differences between pH treatments.}
  \\label{fig:tpc_metrics}
\\end{figure}
")
```


### Percent of Time Above Thermal Optimum Under Warming {-}

```{r fig_2_6_sst_distribution, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=5in]{", here::here("figures", "chapter2", "Fig_2_6_SST_Distribution.png"), "}
  \\caption[Percent of time spent above thermal optimum under current and future warming.]{Percent of time spent above $T_{\\text{opt}}$ for current and future warming predictions. Frequency distributions of daily sea surface temperatures (SST) at Newport Beach, CA—the nearest subtidal temperature station (2 meters MLLW)—under present-day conditions and hypothetical warming scenarios assuming temperature distributions remain the same (+2$^\\circ$C and +4$^\\circ$C). The red dashed line represents the mean SST across the observed period, while the dashed dark red line indicates the thermal optimum averaged between ambient and low pH treatments ($T_{\\text{opt}} = 24.61^\\circ$C) for \\textit{Tegula funebralis}. Yellow bars indicate days below $T_{\\text{opt}}$, and orange bars represent days exceeding $T_{\\text{opt}}$.}
  \\label{fig:sst_distribution}
\\end{figure}
")
```

 In a simple analysis of future shifts in temperature distributions, \textit{Tegula} currently experiences temperatures that exceed their $T_{\text{opt}}$ approximately 0.29\% of the time. However, if sea surface temperatures were to rise by an additional 2$^\circ$C or 4$^\circ$C, as predicted to occur by the end of the century, the percentage of temperatures exceeding $T_{\text{opt}}$ would increase to 2.62\% and 20.1\%, respectively.

### Exposure to Ocean Acidification Increases Energetic Expenditure {-}

```{r fig_2_7_energetic_expenditure, results='asis', echo=FALSE}
cat("
\\begin{figure}[H]
  \\centering
  \\includegraphics[width=5in]{", here::here("figures", "chapter2", "Fig_2_7_Energetic_Expenditure.png"), "}
  \\caption[Energetic expenditure between ambient and low pH treatments.]{Energetic expenditure between ambient and low pH treatments. (A) Box plot illustrating energy expenditure (J g$^{-1}$ h$^{-1}$) across temperature treatments from 12--26$^\\circ$C, colored by pH levels (ambient = orange, low = cyan). Points within the boxes represent the means, and whiskers indicate 1.5 times the interquartile range. (B) Bar plot showing pairwise differences in energetic expenditure between pH treatments at each temperature, based on Two-Way ANOVA results with $\\pm$95\\% confidence intervals. Red bars represent increases, and yellow bars represent decreases in energetic expenditure. Statistically significant pairwise differences, Bonferroni-adjusted, are marked with asterisks; double asterisks denote $p$-values $< 0.01$.}
  \\label{fig:energetic_expenditure}
\\end{figure}
")
```

 A Two-Way ANOVA demonstrated a significant interaction between temperature and pH treatments on the energy requirements of \textit{Tegula funebralis} (F(7, 44) = 2.95, $p <$ 0.05), indicating that the effect of pH on energy expenditure varied by temperature. Pairwise comparisons showed that energetic expenditure was significantly lower in the low pH treatment compared to the ambient pH treatment at both 22$^\circ$C ($p <$ 0.01) and 24$^\circ$C ($p <$ 0.01).

## Discussion {-}

 My findings elucidate the complex interplay between temperature and pH on organismal respiration, demonstrating that while temperature was the primary determinant of metabolic rates, ocean acidification also played a significant role in respiration rates and, thus, energetic expenditure near thermal optima. The combined effects of multiple stressors often lead to nonlinear and unpredictable outcomes, making it challenging to isolate the impact of increased energetic demands alone (Côté et al., 2016; Pörtner, 2012b; Sokolova, 2013). My findings align with ecological theories such as the Metabolic Theory of Ecology (MTE) and Oxygen- and Capacity-Limited Thermal Tolerance (OCLTT) framework, that suggest that integrating multiple aspects of global change, like ocean acidification, increases the energetic expenditure necessary to maintain physiological homeostasis and has the potential to shift physiological metrics (Brown et al., 2004; Pörtner et al., 2017).

 The elevated respiration rates observed in \textit{Tegula funebralis} in response to ocean acidification in this study highlight the complex nonlinear physiological responses placed on marine organisms by multiple drivers of environmental change. The variability in metabolic rates, particularly the marked differences in the maximum metabolic rate ($R_{\text{max}}$) between the ambient and low pH treatments at thermal performance optima, elucidates the utility of thermal performance curves as a powerful approach for assessing multi-stressor interactions that would otherwise go uncovered. Under low pH conditions, the mean $R_{\text{max}}$ was approximately 50\% higher than in ambient pH, illustrating a strong interaction between temperature and pH at physiological optima. These values are consistent with previous research on \textit{Tegula funebralis} (Jellison, Personal Communication; Paine, 1971), including similar species such as \textit{Littorina littorea} and \textit{Haliotis rufescens}, which have shown increased metabolic rates under acidified conditions (Michaelidis et al., 2005; Lannig et al., 2010), thus building confidence that these values are reasonable and expected.

 One possible explanation for the increased metabolic rate exhibited by \textit{T. funebralis} is a compensatory response to the adverse costs of calcification induced by ocean acidification. It is plausible that the species is augmenting its metabolic rate as a means of upholding vital functions and maintaining homeostasis amidst acidic conditions. Higher aerobic respiration results in more ATP production, meeting higher energy costs associated with environmental stressors, a common compensatory mechanism observed in marine invertebrates. Additionally, the upregulation of metabolic pathways that generate ATP to meet the increased energy demands at higher temperatures, such as building calcified shell structures, compensating for changes in acid-base regulation, or contending with shell dissolution, could contribute to this increased metabolic rate (Barclay et al., 2019; Barclay et al., 2020; Brockington and Clarke, 2001; Michaelidis et al., 2005c; Swezey et al., 2020). Furthermore, higher energy demands potentially compromise the energy available for other critical biological processes such as growth, reproduction, and protein synthesis. Increased energetic demand could further impair the ability to produce heat-shock proteins and other protective measures, reducing the capacity to survive extreme temperatures (Pörtner, 2010; Stenseng et al., 2005).

 Despite no significant shifts in optimal temperature ($T_{\text{opt}}$) or other TPC metrics across treatments, slight, but non-significant, reductions in thermal breadth ($T_{\text{br}}$) and increases in $R_{\text{max}}$ under ocean acidification conditions align with our hypothesis and theoretical predictions. Moreover, there was a slight increase in activation energy ($E_a$), indicating higher energetic costs to maintain physiological functions in more acidic environments. These slight differences may have become clearer with a higher sample size or a longer exposure period. Additionally, the $Q_{10}$ temperature coefficient values obtained align with Paine’s (1971) value of 2.64, with a higher $Q_{10}$ at low pH reflecting increased temperature sensitivity and demonstrating that the metabolic rate of \textit{T. funebralis} increases more rapidly with temperature in response to ocean acidification. The present study found that the respiration rate of \textit{T. funebralis} is highest between 24--25$^\circ$C, which is higher than other thermal performance studies of the species that have identified the thermal optimum to be around 20--22$^\circ$C in northern distributions of the species (Tepler et al., 2011; Tomanek and Somero, 1999). Notably, pH had the strongest impact on \textit{Tegula} energy expenditure at or near the snail’s thermal optima, increasing energetic demands under more acidic conditions.

 Understanding the impact of environmental changes, particularly temperature fluctuations and ocean acidification, on the organismal physiology of marine organisms is crucial for predicting their response to climate change. Previous studies have shown that \textit{T. funebralis} has a wider thermal tolerance range compared to its congeners, with a lethal temperature where 50\% of the population faces mortality (LT$_{50}$) at 42.5$^\circ$C, whereas \textit{T. brunnea} and \textit{T. montereyi}, which inhabit lower intertidal and subtidal zones, have an LT$_{50}$ of 36$^\circ$C (Tomanek and Somero, 1999). Despite this broader thermal tolerance, \textit{T. funebralis} may be more vulnerable to future environmental changes, as it endures significant temperature fluctuations within the intertidal zone, often experiencing temperatures at or near its thermal limit within summer months (Stenseng et al., 2005; Tomanek and Sanford, 2003). This could mean that even subtle increases in temperature could push it beyond its physiological limits, making the species more susceptible to the anomalous events, such as marine and terrestrial heatwaves, associated with a changing climate. In a simple analysis of future shifts in temperature distributions, \textit{Tegula} currently experiences temperatures that exceed their $T_{\text{opt}}$ approximately less than 1\% of the time. However, if sea surface temperatures were to rise by an additional 2$^\circ$C or 4$^\circ$C, as predicted to occur by the end of the century (IPCC, 2023), the percentage of temperatures exceeding $T_{\text{opt}}$ would increase to nearly 3\% and 20\%, respectively. This suggests that future warming will substantially increase the thermal stress experienced by \textit{Tegula funebralis}, potentially impacting its survival and fitness. Coping with desiccation and heat stress requires significant energy, particularly for physiological processes like the synthesis of heat-shock proteins and maintaining cellular homeostasis in intertidal organisms such as the black turban snail, \textit{Tegula funebralis} (Tomanek, 2002; Tomanek and Somero, 2002). Increased overall energetic demand may limit \textit{Tegula}'s ability to allocate sufficient energy to these stress responses. Furthermore, increased energetic demands could impair its ability to produce heat-shock proteins and other protective measures, reducing \textit{Tegula}'s capacity to survive extreme temperatures (Pörtner, 2010; Stenseng et al., 2005). Chronic exposure to heat stress, combined with increased energetic costs, could reduce \textit{Tegula}'s long-term viability in higher intertidal zones, potentially leading to shifts in its vertical distribution.

 Significant changes in energy expenditure may have profound ecological implications, potentially triggering cascading consequences for other species within intertidal ecosystems. As a generalist herbivore and detritivore species, the black turban snail consumes an array of macroalgae, microalgae, and kelp wrack (Ricketts et al., 1985; Steinberg, 1985) and their populations play a crucial role in energy transfer within intertidal ecosystems. Temperature- and ocean acidification-induced changes will affect rates of herbivory, affecting the abundance and distribution of algae, influencing the availability of space for other intertidal organisms, and altering predator-prey dynamics (Lubchenco, 1983; Yee, 2002; Nielson, 2001). This is particularly crucial as the macroalgal-herbivore interaction is the primary pathway for energy to move through trophic levels (Lubchenco and Gaines, 1981; O’Connor et al., 2009). Increased energy demands may require \textit{T. funebralis} to forage more actively and for longer periods, potentially increasing their exposure to predators and altering the algal dynamics of the ecological communities they inhabit, thereby impacting species through indirect interactions (Kroeker and Sanford, 2022; Lubchenco, 1983). Furthermore, changes in the energetic costs for \textit{Tegula}'s growth will impact both the size and structural integrity of the shells organisms produce, as evidenced by historical body size declines (Elahi et al., 2020; Barclay et al., 2019) and predator-prey experiments (Jellison and Gaylord, 2019), thereby rendering them more susceptible to predation due to alterations in optimal foraging rankings (Jellison et al., 2022; Kroeker, Sanford, et al., 2014). 

 Given \textit{Tegula}'s pivotal role in energy transfer and its ubiquity in intertidal ecosystems across the Pacific North American coastline, even slight changes in their energy budget could reverberate throughout the food web and indirectly impact species interactions.The annual consumption rate from a study in the Pacific Northwest was estimated at around 1,071 kcal m$^{-2}$ yr$^{-1}$, while the net primary production was about 1,167 kcal m$^{-2}$ yr$^{-1}$, with approximately 60\% of energy transferred to decomposers, illustrating \textit{Tegula}'s critical role in balancing and transferring energy throughout the ecosystem (Paine, 1971). Paine’s (1969) seminal research on the keystone species concept was formulated through the \textit{Pisaster}-\textit{Tegula} interaction, illustrating how changes in the distribution of one species could cascade through the ecosystem, affecting species interactions and community structure (Paine, 1969). These impacts extend to other abundant species within intertidal ecosystems, such as \textit{Pagurus} sp. and \textit{Crepidula} sp., which utilize gastropod shells as a form of habitat specialization (Vermeij, 2020), through cooperative evolutionary strategies (Evans, 1992; Hahn, 1998; Mesce, 1993) with \textit{P. samuelis} and \textit{C. adunca} showing specific preferences for \textit{Tegula funebralis} shells. The reproductive fitness of these species is directly tied to the size, strength, and availability of these shells (Barclay et al., 2019; Gaylord et al., 2019; Taylor, 1981). Consequently, changes within one species could impact not only the biological rates and processes within its population but also extend to impacts on a network of species interactions that no theory could fully summarize.

 Energetic changes induced by ocean acidification in \textit{Tegula funebralis} provide an example of broader ecological shifts. Treating concurrent changes as isolated phenomena is insufficient; embracing multiple interactions allows researchers to examine non-linear responses and determine if these interactions result in ecological surprises (Paine et al., 1998; Darling and Côté, 2008; Kroeker et al., 2017), thereby gaining better predictive power over future scenarios. As marine environments continue to warm and acidify, the metabolic costs for a wide range of species are expected to increase, leading to shifts in species distributions, species interactions, and community structure (Jellison et al., 2016; Kroeker et al., 2012; Kroeker, Sanford, et al., 2014; Pinsky et al., 2013). These changes could fundamentally disrupt the ecological balance and function of marine ecosystems. Alterations in metabolic rates of performance, such as respiration, calcification, and growth attributed to climate change, will cascade to affect net ecosystem production, net ecosystem calcification, food web dynamics, and ultimately the ecosystems humanity relies on.

